Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed

### 2023-02-20 outputs/paper/paper.qmd
Edits to bibliography

## Alberta: Investigating its population ratio, dating markets and anti-refugee sentiments

To investigate the relevance of Dancygier, Egami, Jamal, and Rischke's discoveries in a Canadian context, we will now explore Canada's only Province with a higher ratio of males than females. 
Alberta is a Province in Canada with a total population of 4,543,111 individuals. It is the only Canadian Province that is more heavily populated by males, with a male population of 2,282,040 compared to 2,261,071 females, thus having a ratio of approximately 1.01, which is comparable to that of the 1st tercile in Figure 1 (cite stats 1). This means that there are about 11,000 more men than women residing in this Province. Part of the population gap can be explained by age, as Alberta has a primarily young population, we typically see that as populations age they exhibit a higher female population (cite Edmonton journal). Its trades centric economy also attracts male migrants from across Canada (cite Edmonton journal). Concerning the original paper, Alberta's population growth can be largely attributed to international immigration which has typically brought equal numbers of both males and females (cite Edmonton journal). However, according to the 2021 census, 101, 650 more males are single (not married or living common law and never married) than women (cite statcan). Due to Alberta's young population, highly concentrated with men of working age, a comparison can be made to the term ‘mating-aged’ used in the original paper to describe higher tensions of dating competition.  We thus believe that similar conditions for dating and marriage markets can be made between Alberta and the German municipalities of that the 1st Tercile from Figure 1. 
While population demographics are comparable between that of Alberta and the 1st tercile of German municipalities in the original paper, it is difficult to suggest that potential competition in Albertan dating and marriage markets correlates to anti-refugee sentiments and violence. However, in addressing Albertan immigrant and refugee statistics we will aim to illustrate how these patterns found in Germany can manifest in the context of Alberta. 
Based on the 2021-2022 Annual Population Report, Alberta welcomed 12,603 immigrants and 21,434 non-permanent residents, which include refugees (cite alberta.ca). While previous accounts have suggested that immigration has brought an equal number of males and females, it is safe to assume that Alberta is a growing population, subject to a population with a higher concentration of males (cite Edmonton journal). According to a 2018 paper, at the time 6 in 10 Canadians disagreed when asked if immigration levels were too high, with 35% believing that Canada accepts too many immigrants (cite the globe and mail). However, sentiments appear less than positive in Alberta, with Albertans expressing harsher attitudes towards immigrants and refugees (cite the globe and mail). 48% of Albertans at the time agreed that refugee claims are not filed from real refugees, with 62% stating that immigrants do not adopt Canadian values, about 10% higher than the national average of 51% (cite globe and mail). The globe and mail suggest that part of Alberta's higher anti-refugee attitudes can be attributed to its economy and fears of competition. We also see that in  Dancygier, Egami, Jamal, and Rischke's paper, they find that in areas where men significantly outnumber women, there are higher levels of anti-refugee hate crimes (cite main paper). Based on these statistics, we believe that it is possible that Alberta can be experiencing a similar effect of anti-refugee sentiments in part as a result of increased immigrants/ refugees and competition in a young male-dominated population. However, as stated in their original paper, far more research has to be conducted on this effect to get a better understanding of its implications on non-German countries.

>>>>

## Alberta: Investigating its population ratios, dating markets and anti-refugee sentiments

To investigate the relevance of Dancygier, Egami, Jamal, and Rischke's discoveries in a Canadian context, we will now explore Canada's only Province with a higher ratio of males than females. Alberta is a Province in Canada with a total population of 4,543,111 individuals. It is the only Canadian Province that is more heavily populated by males, with a male population of 2,282,040 compared to 2,261,071 females, thus having a ratio of approximately 1.01, which is comparable to that of the 1st tercile in Figure 1 [@statista]. This means that there are about 11,000 more men than women residing in this Province. Part of the population gap can be explained by age, as Alberta has a primarily young population, we typically see that as populations age they exhibit a higher female population [@edmonton_journal]. Its trades centric economy also attracts male migrants from across Canada [@edmonton_journal]. Concerning the original paper, Alberta's population growth can be largely attributed to international immigration which has typically brought equal numbers of both males and females [@edmonton_journal]. However, according to the 2021 census, 101, 650 more males are single (not married or living common law and never married) than women [@govcan]. Due to Alberta's young population, highly concentrated with men of working age, a comparison can be made to the term 'mating-aged' used in the original paper to describe higher tensions of dating competition. We thus believe that similar conditions for dating and marriage markets can be made between Alberta and the German municipalities of that the 1st Tercile from Figure 1. While population demographics are comparable between that of Alberta and the 1st tercile of German municipalities in the original paper, it is difficult to suggest that potential competition in Albertan dating and marriage markets correlates to anti-refugee sentiments and violence. However, in addressing Albertan immigrant and refugee statistics we will aim to illustrate how these patterns found in Germany can manifest in the context of Alberta. Based on the 2021-2022 Annual Population Report, Alberta welcomed 12,603 immigrants and 21,434 non-permanent residents, which include refugees [@alberta_2023]. While previous accounts have suggested that immigration has brought an equal number of males and females, it is safe to assume that Alberta is a growing population, subject to a population with a higher concentration of males [@edmonton_journal]. According to a 2018 paper, at the time 6 in 10 Canadians disagreed when asked if immigration levels were too high, with 35% believing that Canada accepts too many immigrants [@globe_mail]. However, sentiments appear less than positive in Alberta, with Albertans expressing harsher attitudes towards immigrants and refugees [@globe_mail]. 48% of Albertans at the time agreed that refugee claims are not filed from real refugees, with 62% stating that immigrants do not adopt Canadian values, about 10% higher than the national average of 51% [@globe_mail]. The globe and mail suggest that part of Alberta's higher anti-refugee attitudes can be attributed to its economy and fears of competition. We also see that in Dancygier, Egami, Jamal, and Rischke's paper, they find that in areas where men significantly outnumber women, there are higher levels of anti-refugee hate crimes [@main_paper]. Based on these statistics, we believe that it is possible that Alberta can be experiencing a similar effect of anti-refugee sentiments in part as a result of increased immigrants/ refugees and competition in a young male-dominated population. However, as stated in their original paper, far more research has to be conducted on this effect to get a better understanding of its implications on non-German countries.
